Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Impose hard wrapping on abstract
Ensure appendix doesn't render
Edits to intro

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
appendix          : "appendix.Rmd"

@@

Social coordination has long been used both physically and virtually
to start and carry out collective actions. These collective events
bring individuals together and create emergent patterns of communication
and action. Online communication has historically been used to document
and communicate archival information about events, but it has been
increasingly used to bring about social change. From a dynamical
systems perspective, these different means of social coordination during
times of turmoil can be considered two complementary components of a
single system, mutually constrained and constantly interacting and
influencing one another [@mahner1997foundations]. Investigation of the
coupling of real-world mobilization and social cohesion could provide
new insight into the power of social media during mobilization and the
ways in which individuals utilize it to bring about, or respond to, social
change. Increasingly, social media platforms are being utilized during
social mobilization, but the relationship between virtual and real-world
mobilization is still largely unknown. The present work aims to understand
how physical and virtual movements coexist and interact from a dynamical
systems perspective.

>>>>

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
appendix          :

@@

Social coordination has long been used both physically and virtually
to start and carry out collective actions. These collective events
bring individuals together and create emergent patterns of communication
and action. From a dynamical
systems perspective, these different means of social coordination during
times of turmoil can be considered two complementary components of a
single system, mutually constrained and constantly interacting and
influencing one another [@mahner1997foundations]. 
Increasingly, social media platforms are being utilized during
social mobilization, but the relationship between virtual and real-world
mobilization is still largely unknown. Investigation of the
coupling of real-world mobilization and social cohesion could provide
new insights into the power of social media during mobilization and 
it can be used to respond to or create social change. The present work 
aims to understand how physical and virtual movements coexist and interact 
from a dynamical systems perspective.
